Presentasjon OPX Fiffig tittel

### 2022-08-03 Presentasjon/Presentasjon v3.Rmd
Presentasjon mock
Oppdatert mock

---
title: "Presentasjon OPX Fiffig tittel"
author: "Gruppe 5"
date: "4.8.2022"
output: 
  ioslides_presentation: 
    css: stylesss.css
---

@@

#brns_items
#opx_items

@@

>>>>

---
title: "Presentasjon OPX Fiffig tittel"
author: "Group 5: Aga, Amalie, Henrik, Ida, Torbjørn"
date: "2022-08-04"
output: 
  ioslides_presentation:
    widescreen: TRUE 
    css: stylesss.css
---

@@

## Items Brønnøysund
```{r, out.height="470", out.width="800", fig.align='center'}
knitr::include_graphics("Images/Brns_items.png")

## Items OPX
```{r, out.height="514", out.width="710", fig.align='center'}
knitr::include_graphics("Images/OPX_items.png")

@@

# Dashboard

# Limitations and steps forward
